### 2022-03-05 paper/output/document/appendix.tex
added will's fixes to ch5

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, no one is a moral exception.
Formalizing this interpretation requires using open sentences to handle the notion of substitution.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{In English, this statement roughly means that, if action $A$ is 
permissible for some person $p$, then, for any person $p$, action $A$ must be permissible. The notion of ``permissible $for$" 
is captured by the substitution of $x$ for $p$.%
}%
\begin{isamarkuptext}%
Let's check if this is already an axiom of DDL. If so, then the formalization is trivial.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ FUL{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ FUL\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:

  Skolem constants:
    A = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := True), $s_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
    p = $s_1$
    x = $s_2$\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This formalization doesn't hold in DDL, so adding it as an axiom will change the logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\ FUL{\isacharcolon}\ FUL%
\begin{isamarkuptext}%
Consistency check: is the logic still consistent with the FUL added as an axiom?%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ True\ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ satisfy{\isacharcomma}\ card{\isacharequal}{\isadigit{1}}{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpicking formula... 
Nitpick found a model for card i = 1:

  Empty assignment\color{black}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent. Now it's time to start testing!%
\isamarkupsubsubsection{Application Tests\label{sec:app_tests_kroy}%
In the following sections, I will use the application and metaethical tests presenting in Sections \ref{sec:app_tests_naive} and \ref{sec:meta_tests_naive}
        to tease out the strengths and weaknesses of Kroy's formalization. While the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means. 
        I will analyze these problems in the context of philosophical scholarship explicating the content 
        of the formula of universal law. The findings in these sections will inform milestones for my
        custom formalization of the categorical imperative. They also serve as an example of how formalized
        and automated ethics can reveal philosophical strengths and weaknesses of an ethical theory.%
\textbf{Murder}%
In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
it is actually wrong.%
\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
will begin to take on features of the act of murder when I specify its properties. In the tests below, 
I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
defined in Isabelle—they have no meaning until I program a meaning.%
\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
at all worlds.%
This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
to imply prohibition at $\text{every world}$.

@@

%:%400=242%:%
%:%401=242%:%
%:%403=243%:%
%:%404=244%:%
%:%405=245%:%
%:%408=247%:%
%:%410=249%:%
%:%411=249%:%
%:%412=250%:%
%:%413=251%:%
%:%414=251%:%
%:%416=251%:%
%:%420=251%:%
%:%421=251%:%
%:%423=252%:%
%:%424=253%:%
%:%425=254%:%
%:%426=255%:%
%:%427=256%:%
%:%428=257%:%
%:%438=259%:%

@@

%:%441=261%:%
%:%443=263%:%
%:%445=265%:%
%:%446=265%:%
%:%447=265%:%
%:%449=265%:%
%:%453=265%:%
%:%454=265%:%
%:%456=266%:%
%:%457=267%:%
%:%458=268%:%
%:%459=269%:%
%:%469=271%:%
%:%470=272%:%
%:%471=273%:%
%:%472=274%:%

@@

%:%505=289%:%
%:%509=291%:%

@@

%:%511=293%:%
%:%513=295%:%
%:%514=295%:%
%:%516=296%:%
%:%517=297%:%
%:%518=298%:%
%:%519=299%:%
%:%520=300%:%
%:%521=301%:%
%:%522=302%:%
%:%523=302%:%
%:%524=303%:%
%:%525=304%:%
%:%526=304%:%
%:%527=305%:%
%:%530=306%:%
%:%534=306%:%
%:%535=306%:%
%:%537=307%:%
%:%538=308%:%
%:%548=310%:%

@@

%:%550=312%:%
%:%551=313%:%
%:%552=314%:%
%:%553=315%:%
%:%554=316%:%
%:%555=317%:%
%:%556=318%:%
%:%557=319%:%
%:%558=320%:%
%:%559=321%:%
%:%560=322%:%
%:%561=323%:%
%:%562=324%:%
%:%563=325%:%
%:%564=326%:%
%:%565=327%:%
%:%569=329%:%
%:%570=330%:%
%:%572=332%:%
%:%573=332%:%
%:%575=333%:%
%:%576=333%:%
%:%577=334%:%
%:%578=335%:%
%:%579=335%:%
%:%580=336%:%
%:%583=337%:%
%:%587=337%:%
%:%588=337%:%
%:%589=338%:%
%:%590=338%:%
%:%591=339%:%
%:%592=339%:%
%:%593=340%:%
%:%594=340%:%
%:%595=340%:%
%:%596=341%:%
%:%606=343%:%
%:%607=344%:%
%:%608=345%:%
%:%609=346%:%
%:%613=348%:%
%:%617=350%:%
%:%618=351%:%
%:%619=352%:%
%:%623=354%:%
%:%624=355%:%
%:%626=357%:%
%:%627=357%:%
%:%640=378%:%
%:%641=379%:%
%:%642=379%:%
%:%644=380%:%
%:%645=381%:%
%:%646=382%:%
%:%647=383%:%
%:%648=384%:%
%:%649=385%:%
%:%650=385%:%
%:%652=386%:%
%:%653=387%:%
%:%654=387%:%
%:%655=388%:%
%:%656=389%:%
%:%657=389%:%
%:%659=390%:%
%:%660=391%:%
%:%663=393%:%
%:%664=394%:%
%:%666=396%:%
%:%667=396%:%
%:%668=397%:%
%:%669=398%:%
%:%670=398%:%
%:%672=398%:%
%:%676=398%:%
%:%677=398%:%
%:%679=399%:%
%:%680=400%:%
%:%681=401%:%
%:%682=402%:%
%:%683=403%:%
%:%684=404%:%
%:%685=405%:%
%:%695=407%:%
%:%696=408%:%
%:%697=409%:%
%:%700=411%:%
%:%701=412%:%
%:%702=413%:%
%:%703=414%:%
%:%704=415%:%
%:%705=416%:%
%:%708=418%:%
%:%710=420%:%
%:%711=420%:%
%:%712=421%:%
%:%715=422%:%
%:%719=422%:%
%:%720=422%:%
%:%722=423%:%
%:%728=423%:%
%:%731=424%:%
%:%732=425%:%
%:%733=425%:%
%:%734=426%:%
%:%735=427%:%
%:%736=428%:%
%:%737=428%:%
%:%739=428%:%
%:%743=428%:%
%:%744=428%:%
%:%746=429%:%
%:%747=430%:%
%:%748=431%:%
%:%749=432%:%
%:%750=433%:%
%:%760=435%:%
%:%761=436%:%
%:%762=437%:%
%:%763=438%:%
%:%764=439%:%
%:%765=440%:%
%:%766=441%:%
%:%767=442%:%
%:%768=443%:%
%:%772=446%:%
%:%773=447%:%
%:%774=448%:%
%:%775=449%:%
%:%776=450%:%
%:%777=451%:%
%:%778=452%:%
%:%779=453%:%
%:%780=454%:%
%:%781=455%:%
%:%782=456%:%
%:%783=457%:%
%:%792=459%:%
%:%804=461%:%
%:%805=462%:%
%:%806=463%:%
%:%808=465%:%
%:%809=465%:%
%:%810=466%:%
%:%811=467%:%
%:%812=468%:%
%:%813=468%:%
%:%815=468%:%
%:%819=468%:%
%:%820=468%:%
%:%822=469%:%
%:%823=470%:%
%:%824=471%:%
%:%825=472%:%
%:%835=474%:%
%:%836=475%:%
%:%837=476%:%
%:%841=478%:%
%:%843=480%:%
%:%844=480%:%
%:%845=481%:%
%:%846=482%:%
%:%847=483%:%
%:%848=483%:%
%:%850=483%:%
%:%854=483%:%
%:%855=483%:%
%:%857=484%:%
%:%858=485%:%
%:%859=486%:%
%:%860=487%:%
%:%870=489%:%
%:%871=490%:%
%:%873=492%:%
%:%874=492%:%
%:%875=493%:%
%:%876=494%:%
%:%877=495%:%
%:%878=495%:%
%:%880=495%:%
%:%884=495%:%
%:%885=495%:%
%:%887=496%:%
%:%888=497%:%
%:%889=498%:%
%:%890=499%:%
%:%891=500%:%
%:%901=502%:%
%:%902=503%:%
%:%904=505%:%
%:%905=505%:%
%:%906=506%:%
%:%907=507%:%
%:%910=508%:%
%:%914=508%:%
%:%915=508%:%
%:%916=508%:%
%:%925=510%:%
%:%926=511%:%
%:%927=512%:%
%:%928=513%:%
%:%930=515%:%
%:%931=515%:%
%:%932=516%:%
%:%933=517%:%
%:%936=518%:%
%:%940=518%:%
%:%941=518%:%
%:%942=518%:%
%:%951=520%:%
%:%952=521%:%
%:%954=523%:%

@@

%:%956=524%:%
%:%957=525%:%
%:%958=526%:%
%:%959=526%:%
%:%961=526%:%
%:%965=526%:%
%:%966=526%:%
%:%968=527%:%
%:%969=528%:%
%:%970=529%:%
%:%971=530%:%
%:%981=532%:%
%:%982=533%:%
%:%983=534%:%
%:%984=535%:%
%:%985=536%:%
%:%986=537%:%
%:%988=539%:%
%:%989=539%:%
%:%990=540%:%
%:%991=541%:%
%:%992=542%:%
%:%993=543%:%
%:%994=543%:%
%:%996=543%:%
%:%1000=543%:%
%:%1001=543%:%
%:%1003=544%:%
%:%1004=545%:%
%:%1005=546%:%
%:%1006=547%:%
%:%1007=548%:%
%:%1008=549%:%
%:%1018=551%:%
%:%1019=552%:%
%:%1020=553%:%
%:%1021=554%:%
%:%1022=555%:%
%:%1023=556%:%
%:%1025=558%:%
%:%1026=558%:%
%:%1027=559%:%
%:%1028=560%:%
%:%1031=561%:%
%:%1035=561%:%
%:%1036=561%:%
%:%1038=562%:%
%:%1048=564%:%
%:%1049=565%:%
%:%1051=566%:%
%:%1052=566%:%
%:%1053=567%:%
%:%1054=568%:%
%:%1055=568%:%
%:%1057=568%:%
%:%1061=568%:%
%:%1062=568%:%
%:%1064=569%:%
%:%1065=570%:%
%:%1066=571%:%
%:%1067=572%:%
%:%1068=573%:%
%:%1091=579%:%
%:%1092=580%:%
%:%1093=581%:%
%:%1094=582%:%
%:%1103=584%:%
%:%1115=586%:%
%:%1116=587%:%
%:%1117=588%:%
%:%1118=589%:%
%:%1122=591%:%
%:%1123=592%:%
%:%1125=594%:%
%:%1126=594%:%
%:%1127=595%:%
%:%1128=596%:%
%:%1129=596%:%
%:%1130=597%:%
%:%1133=598%:%
%:%1137=598%:%
%:%1138=598%:%
%:%1139=598%:%
%:%1141=599%:%
%:%1142=600%:%
%:%1152=602%:%
%:%1153=603%:%
%:%1154=604%:%
%:%1155=605%:%
%:%1156=606%:%

>>>>

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, 
no one is a moral exception.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{If action $A$ is permissible for some person, then, for any person $p$, action $A$ must be 
permissible for $p$. The notion of ``permissible for'' 
is captured by the substitution of $x$ for $p$.%
}%
\begin{isamarkuptext}%
This formalization does not hold in DDL, the base logic. This means that Kroy's formalization
already passes one test, and that adding it as an axiom will strengthen the logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ FUL{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ FUL\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:

  Skolem constants:
    A = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := True), $s_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False))
    p = $s_1$
    x = $s_2$\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
\isanewline
\isanewline
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\ FUL{\isacharcolon}\ FUL%
\begin{isamarkuptext}%
Now that I have added Kroy's formalization of the FUL as an axiom, I will check that it is 
consistent by looking for a model that satisfies it and all the other axioms of DDL.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ True\ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ satisfy{\isacharcomma}\ card{\isacharequal}{\isadigit{1}}{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpicking formula... 
Nitpick found a model for card i = 1:

  Empty assignment\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Testing Kroy's Formalization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I use my testing framework to evaluate Kroy's formalization. I find that, while 
        the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means.

        I already showed above that Kroy's formalization is stronger than DDL. Next, I test whether or
not obligations universalize across people. This test passes, aperhaps trivially, due to the fact that 
this property is definitionally the basis of Kroy's formalization; his formalization states, intuitively, 
that obligations must hold across all people.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ obligation{\isacharunderscore}universalizes{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymforall}p{\isachardot}\ O\ {\isacharbraceleft}A\ p{\isacharbraceright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}true{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
\noindent \textbf{Murder}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
In Section \ref{sec:app_tests_naive}, I began by testing the naive interpretation's ability to show that murder 
is wrong. I started by showing the morally dubious proposition that if murder is possibly wrong, then 
it is actually wrong.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{consts}\isamarkupfalse%
\ M{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Let the constant $M$ denote murder. I have defined no features of this constant, except that it is 
of the type term, which can be true or false at a set of worlds. Indeed, this constant as-is has no 
semantic meaning and could be replaced with any symbol, like `Q' or `Going to Target.' This constant 
will begin to take on features of the act of murder when I specify its properties. In the tests below, 
I specify its properties as the antecedents of lemmas. For example, the test below specifies that 
it is possible that murder is prohibited at the current world. This pattern will hold for most constants 
defined in Isabelle—they have no meaning until I program a meaning.%
}\isanewline
\isanewline
\isacommand{lemma}\isamarkupfalse%
\ wrong{\isacharunderscore}if{\isacharunderscore}possibly{\isacharunderscore}wrong{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}{\isasymdiamond}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ cw{\isacharparenright}\ {\isasymlongrightarrow}\ \ {\isacharparenleft}{\isasymforall}w{\isachardot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ M{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{This sentence reads: ``If it is possible that murder is prohibited at world cw, then murder is prohibited 
at all worlds.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This is the same result we got in Section \ref{sec:app_tests_naive}—if murder is possibly wrong at some world, it is wrong at
every world. The result is incredible strong—the mere possibility of wrongness at some world is sufficient
to imply prohibition at $\text{every world}$.

@@

%:%400=243%:%
%:%401=243%:%
%:%403=244%:%
%:%404=245%:%
%:%405=246%:%
%:%408=248%:%
%:%409=249%:%
%:%411=251%:%
%:%412=251%:%
%:%413=252%:%
%:%414=253%:%
%:%415=253%:%
%:%417=253%:%
%:%421=253%:%
%:%422=253%:%
%:%424=254%:%
%:%425=255%:%
%:%426=256%:%
%:%427=257%:%
%:%428=258%:%
%:%429=259%:%
%:%437=259%:%
%:%438=260%:%
%:%439=261%:%

@@

%:%442=263%:%
%:%443=264%:%
%:%445=266%:%
%:%446=266%:%
%:%447=266%:%
%:%449=266%:%
%:%453=266%:%
%:%454=266%:%
%:%456=267%:%
%:%457=268%:%
%:%458=269%:%
%:%459=270%:%
%:%469=272%:%
%:%470=273%:%
%:%471=274%:%
%:%472=275%:%

@@

%:%502=288%:%
%:%504=290%:%
%:%505=290%:%
%:%506=291%:%
%:%507=292%:%
%:%508=292%:%

@@

%:%514=292%:%
%:%524=294%:%
%:%528=296%:%
%:%529=297%:%
%:%530=298%:%
%:%532=300%:%
%:%533=300%:%
%:%535=301%:%
%:%536=302%:%
%:%537=303%:%
%:%538=304%:%
%:%539=305%:%
%:%540=306%:%
%:%541=307%:%
%:%542=307%:%
%:%543=308%:%
%:%544=309%:%
%:%545=309%:%
%:%546=310%:%

@@

%:%553=311%:%
%:%554=311%:%
%:%556=312%:%
%:%557=313%:%
%:%567=315%:%
%:%568=316%:%
%:%569=317%:%
%:%570=318%:%
%:%571=319%:%
%:%572=320%:%
%:%573=321%:%
%:%574=322%:%
%:%575=323%:%
%:%576=324%:%
%:%577=325%:%
%:%578=326%:%
%:%579=327%:%
%:%580=328%:%
%:%581=329%:%
%:%582=330%:%
%:%583=331%:%
%:%584=332%:%
%:%588=334%:%
%:%589=335%:%
%:%591=337%:%
%:%592=337%:%
%:%594=338%:%
%:%595=338%:%
%:%596=339%:%
%:%597=340%:%
%:%598=340%:%
%:%599=341%:%
%:%602=342%:%
%:%606=342%:%
%:%607=342%:%
%:%608=343%:%
%:%609=343%:%
%:%610=344%:%
%:%611=344%:%
%:%612=345%:%
%:%613=345%:%
%:%614=345%:%
%:%615=346%:%
%:%625=348%:%
%:%626=349%:%
%:%627=350%:%
%:%628=351%:%
%:%632=353%:%
%:%636=355%:%
%:%637=356%:%
%:%638=357%:%
%:%642=359%:%
%:%643=360%:%
%:%645=362%:%
%:%646=362%:%
%:%659=383%:%
%:%660=384%:%
%:%661=384%:%
%:%663=385%:%
%:%664=386%:%
%:%665=387%:%
%:%666=388%:%
%:%667=389%:%
%:%668=390%:%
%:%669=390%:%
%:%671=391%:%
%:%672=392%:%
%:%673=392%:%
%:%674=393%:%
%:%675=394%:%
%:%676=394%:%
%:%678=395%:%
%:%679=396%:%
%:%682=398%:%
%:%683=399%:%
%:%685=401%:%
%:%686=401%:%
%:%687=402%:%
%:%688=403%:%
%:%689=403%:%
%:%691=403%:%
%:%695=403%:%
%:%696=403%:%
%:%698=404%:%
%:%699=405%:%
%:%700=406%:%
%:%701=407%:%
%:%702=408%:%
%:%703=409%:%
%:%704=410%:%
%:%714=412%:%
%:%715=413%:%
%:%716=414%:%
%:%719=416%:%
%:%720=417%:%
%:%721=418%:%
%:%722=419%:%
%:%723=420%:%
%:%724=421%:%
%:%727=423%:%
%:%729=425%:%
%:%730=425%:%
%:%731=426%:%
%:%734=427%:%
%:%738=427%:%
%:%739=427%:%
%:%741=428%:%
%:%747=428%:%
%:%750=429%:%
%:%751=430%:%
%:%752=430%:%
%:%753=431%:%
%:%754=432%:%
%:%755=433%:%
%:%756=433%:%
%:%758=433%:%
%:%762=433%:%
%:%763=433%:%
%:%765=434%:%
%:%766=435%:%
%:%767=436%:%
%:%768=437%:%
%:%769=438%:%
%:%779=440%:%
%:%780=441%:%
%:%781=442%:%
%:%782=443%:%
%:%783=444%:%
%:%784=445%:%
%:%785=446%:%
%:%786=447%:%
%:%787=448%:%
%:%791=451%:%
%:%792=452%:%
%:%793=453%:%
%:%794=454%:%
%:%795=455%:%
%:%796=456%:%
%:%797=457%:%
%:%798=458%:%
%:%799=459%:%
%:%800=460%:%
%:%801=461%:%
%:%802=462%:%
%:%811=464%:%
%:%823=466%:%
%:%824=467%:%
%:%825=468%:%
%:%827=470%:%
%:%828=470%:%
%:%829=471%:%
%:%830=472%:%
%:%831=473%:%
%:%832=473%:%
%:%834=473%:%
%:%838=473%:%
%:%839=473%:%
%:%841=474%:%
%:%842=475%:%
%:%843=476%:%
%:%844=477%:%
%:%854=479%:%
%:%855=480%:%
%:%856=481%:%
%:%860=483%:%
%:%862=485%:%
%:%863=485%:%
%:%864=486%:%
%:%865=487%:%
%:%866=488%:%
%:%867=488%:%
%:%869=488%:%
%:%873=488%:%
%:%874=488%:%
%:%876=489%:%
%:%877=490%:%
%:%878=491%:%
%:%879=492%:%
%:%889=494%:%
%:%890=495%:%
%:%892=497%:%
%:%893=497%:%
%:%894=498%:%
%:%895=499%:%
%:%896=500%:%
%:%897=500%:%
%:%899=500%:%
%:%903=500%:%
%:%904=500%:%
%:%906=501%:%
%:%907=502%:%
%:%908=503%:%
%:%909=504%:%
%:%910=505%:%
%:%920=507%:%
%:%921=508%:%
%:%923=510%:%
%:%924=510%:%
%:%925=511%:%
%:%926=512%:%
%:%929=513%:%
%:%933=513%:%
%:%934=513%:%
%:%935=513%:%
%:%944=515%:%
%:%945=516%:%
%:%946=517%:%
%:%947=518%:%
%:%949=520%:%
%:%950=520%:%
%:%951=521%:%
%:%952=522%:%

@@

%:%959=523%:%
%:%960=523%:%
%:%961=523%:%
%:%970=525%:%
%:%971=526%:%
%:%973=528%:%
%:%974=528%:%
%:%975=529%:%
%:%976=530%:%
%:%977=531%:%
%:%978=531%:%
%:%980=531%:%
%:%984=531%:%
%:%985=531%:%
%:%987=532%:%
%:%988=533%:%
%:%989=534%:%
%:%990=535%:%
%:%1000=537%:%
%:%1001=538%:%
%:%1002=539%:%
%:%1003=540%:%
%:%1004=541%:%
%:%1005=542%:%
%:%1007=544%:%
%:%1008=544%:%
%:%1009=545%:%
%:%1010=546%:%
%:%1011=547%:%
%:%1012=548%:%
%:%1013=548%:%
%:%1015=548%:%
%:%1019=548%:%
%:%1020=548%:%
%:%1022=549%:%
%:%1023=550%:%
%:%1024=551%:%
%:%1025=552%:%
%:%1026=553%:%
%:%1027=554%:%
%:%1037=556%:%
%:%1038=557%:%
%:%1039=558%:%
%:%1040=559%:%
%:%1041=560%:%
%:%1042=561%:%
%:%1044=563%:%
%:%1045=563%:%
%:%1046=564%:%
%:%1047=565%:%
%:%1050=566%:%
%:%1054=566%:%
%:%1055=566%:%
%:%1057=567%:%
%:%1067=569%:%
%:%1068=570%:%
%:%1070=571%:%
%:%1071=571%:%
%:%1072=572%:%
%:%1073=573%:%
%:%1074=573%:%
%:%1076=573%:%
%:%1080=573%:%
%:%1081=573%:%
%:%1083=574%:%
%:%1084=575%:%
%:%1085=576%:%
%:%1086=577%:%
%:%1087=578%:%
%:%1110=584%:%
%:%1111=585%:%
%:%1112=586%:%
%:%1113=587%:%
%:%1122=589%:%
%:%1134=591%:%
%:%1135=592%:%
%:%1136=593%:%
%:%1137=594%:%
%:%1141=596%:%
%:%1142=597%:%
%:%1144=599%:%
%:%1145=599%:%
%:%1146=600%:%
%:%1147=601%:%
%:%1148=601%:%
%:%1149=602%:%
%:%1152=603%:%
%:%1156=603%:%
%:%1157=603%:%
%:%1158=603%:%
